A Survey on Ordered Binary Decision Diagrams

### 2015-09-08 paper.tex
Add tbd macro; Fix typo

\newcommand{\tbr}{\textbf{[TO BE REVISED]}}

@@

Nonetheless representing Boolean function using OBDDs has some drawbacks. Classes
of Boolean functions exist for which the size of the graph grows exponentially,
e.g. integer multiplication~\cite{BRYANT86, BRYANT91, WOELFEL01}.

These limitations of OBDDs motivated researchers to introduce other
representations which e.g. relax the ordering or change the interpretation of
nodes~\cite{BRYANT95}. Such representations may be beneficial for some classes
of Boolean functions but mostly suffer from losing the canonical form and hence
the desirable properties OBDDs are famous for.

@@

Tbd.

@@

\noindent
\par
BRYANT86\cite{BRYANT86},
\par
BRACE90\cite{BRACE90}, BRYANT91\cite{BRYANT91}, BRYANT92\cite{BRYANT92},
\par
RUDELL93\cite{RUDELL93}, BRYANT95\cite{BRYANT95}, BOLLIG96\cite{BOLLIG96},
\par
ANDERSEN97\cite{ANDERSEN97}, WOELFEL01\cite{WOELFEL01}

>>>>

\newcommand{\tbr}{\textbf{[TO BE REVISED]}}
\newcommand{\tbd}{\textbf{[TO BE DONE]}}

@@

Nonetheless representing Boolean functions using OBDDs has some drawbacks. Classes
of Boolean functions exist for which the size of the graph grows exponentially,
e.g. integer multiplication~\cite{BRYANT86, BRYANT91, WOELFEL01}.

These limitations of OBDDs motivated researchers to introduce other
representations which e.g. relax the ordering~\cite{BRYANT95} or change the
interpretation of nodes~\cite{BRYANT95}~\cite{ANDERSEN97}. Such representations
may be beneficial for some classes of Boolean functions but mostly suffer from
losing the canonical form and hence the desirable properties OBDDs are famous for.

@@

\tbd

@@

\noindent
\par
BRACE90\cite{BRACE90}, BRYANT92\cite{BRYANT92},
\par
RUDELL93\cite{RUDELL93}, BOLLIG96\cite{BOLLIG96}
